---
title: "Data Analysis and Visualization <br> Paper 2"
author: Gagan Atreya 
date: today
format:
  html:
    toc: true
    toc-location: left
    toc-depth: 4
    theme: lumenR
    fontsize: large
    code-fold: true
    code-tools: true
    code-summary: "Display code"
    code-overflow: wrap
editor: 
  markdown: 
    wrap: 72
---

# **Section 1. Data importation and cleaning**

```{r, error = F, message=F, warning = F}

## clear environment:
rm(list=ls())
options(digits = 2)

## Correct asterisk pattern for stargazer tables:
starpattern <- "<em>&#42;p&lt;0.05;&nbsp;&#42;&#42;p&lt;0.01;&nbsp;&#42;&#42;&#42;p&lt;0.001</em>"

## Install "pacman" package if not installed
# (remove the # symbol from the line below):
# install.packages("pacman")

## Load R packages:
pacman::p_load(data.table, tidyverse, haven, labelled, vtable, 
               psych, scales, weights, clipr, forcats,
               stargazer, ggthemes, ggcharts, geomtextpath,
               corrplot, tm, readxl, patchwork, modelsummary,
               gt, lme4, car, lmerTest, lavaan,
               ggeffects, magrittr, broom, broom.mixed,
               backports, effects, interactions, plyr, sjPlot)

## Import datasets. These are cleaned datasets with variables created and named in the individual country R scripts:

# Gambia:
dsgmb <- fread("~/Dropbox/2023_Gagan/Paper02/data/dsgmb.csv")

# Pakistan:
dspak <- fread("~/Dropbox/2023_Gagan/Paper02/data/dspak.csv")

# Tanzania:
dstza <- fread("~/Dropbox/2023_Gagan/Paper02/data/dstza.csv")

# Uganda:
dsuga <- fread("~/Dropbox/2023_Gagan/Paper02/data/dsuga.csv")

# Combine into one dataset:
ds <- rbind(dsgmb, dspak, dstza, dsuga)

## Clean demographic variables: 

## gender:
ds$gender <- ifelse(ds$gender == "Male", "Male",
             ifelse(ds$gender == "Female", "Female", NA))

## ses:
ds$ses <- ifelse(ds$ses == "", NA, ds$ses)

## Religion:
ds$religion <- ifelse(ds$religion == "", NA, ds$religion)

ds$religion <- ifelse(ds$religion == "Christian (Catholic)", "Christian: Catholic", 
               ifelse(ds$religion == "Christian (Protestant)", "Christian: Protestant",
               ifelse(ds$religion == "Muslim (Shia)", "Muslim: Shia",
               ifelse(ds$religion == "Muslim (Sunni)", "Muslim: Sunni", ds$religion))))

## Marital status
ds$married <- ifelse(ds$married == "Not married", "Unmarried", ds$married)
ds$married <- ifelse(ds$married == "", NA, ds$married)

## Separate into individual country datasets:
dsgmb <- ds[ds$country == "Gambia", ]
dspak <- ds[ds$country == "Pakistan", ]
dstza <- ds[ds$country == "Tanzania", ]
dsuga <- ds[ds$country == "Uganda", ]

```

### Missing data: Gambia

```{r, error = F, message=F, warning = F}

missing_ds <- map(dsgmb, ~mean(is.na(.))*100) 
missing_ds <- as.data.frame(missing_ds)
missing_ds <- as_tibble(cbind(variable = names(missing_ds), t(missing_ds)))
missing_ds$percent_missing <- missing_ds$V2
missing_ds$percent_missing <- as.numeric(missing_ds$percent_missing)

missing_ds <- select(missing_ds,-c(2))
missing_ds <- as.data.frame(missing_ds)
missing_ds$percent_missing <- as.numeric(missing_ds$percent_missing)
missing_ds <- as.data.table(missing_ds)

missing_ds_01 <- missing_ds[1:31,]
missing_ds_02 <- missing_ds[32:61,]

lp01 <- missing_ds_01 %>%
  lollipop_chart(x = variable,
                 y = percent_missing,
               line_color = "black",
               point_color = "black")+
  labs(y = "% missing data",
       x = "",
       title = "Gambia")+
  theme_bw()

lp02 <- missing_ds_02 %>% 
  lollipop_chart(x = variable,
                 y = percent_missing,
               line_color = "black",
               point_color = "black")+
  labs(y = "% missing data",
       x = "",
       title = "")+
  theme_bw()

lp01| lp02

```

### Missing data: Pakistan

```{r, error = F, message=F, warning = F}

missing_ds <- map(dspak, ~mean(is.na(.))*100) 
missing_ds <- as.data.frame(missing_ds)
missing_ds <- as_tibble(cbind(variable = names(missing_ds), t(missing_ds)))
missing_ds$percent_missing <- missing_ds$V2
missing_ds$percent_missing <- as.numeric(missing_ds$percent_missing)

missing_ds <- select(missing_ds,-c(2))
missing_ds <- as.data.frame(missing_ds)
missing_ds$percent_missing <- as.numeric(missing_ds$percent_missing)
missing_ds <- as.data.table(missing_ds)

missing_ds_01 <- missing_ds[1:31,]
missing_ds_02 <- missing_ds[32:61,]

lp01 <- missing_ds_01 %>%
  lollipop_chart(x = variable,
                 y = percent_missing,
               line_color = "black",
               point_color = "black")+
  labs(y = "% missing data",
       x = "",
       title = "Pakistan")+
  theme_bw()

lp02 <- missing_ds_02 %>% 
  lollipop_chart(x = variable,
                 y = percent_missing,
               line_color = "black",
               point_color = "black")+
  labs(y = "% missing data",
       x = "",
       title = "")+
  theme_bw()

lp01| lp02

```

### Missing data: Tanzania

```{r, error = F, message=F, warning = F}

missing_ds <- map(dstza, ~mean(is.na(.))*100) 
missing_ds <- as.data.frame(missing_ds)
missing_ds <- as_tibble(cbind(variable = names(missing_ds), t(missing_ds)))
missing_ds$percent_missing <- missing_ds$V2
missing_ds$percent_missing <- as.numeric(missing_ds$percent_missing)

missing_ds <- select(missing_ds,-c(2))
missing_ds <- as.data.frame(missing_ds)
missing_ds$percent_missing <- as.numeric(missing_ds$percent_missing)
missing_ds <- as.data.table(missing_ds)

missing_ds_01 <- missing_ds[1:31,]
missing_ds_02 <- missing_ds[32:61,]

lp01 <- missing_ds_01 %>%
  lollipop_chart(x = variable,
                 y = percent_missing,
               line_color = "black",
               point_color = "black")+
  labs(y = "% missing data",
       x = "",
       title = "Tanzania")+
  theme_bw()

lp02 <- missing_ds_02 %>% 
  lollipop_chart(x = variable,
                 y = percent_missing,
               line_color = "black",
               point_color = "black")+
  labs(y = "% missing data",
       x = "",
       title = "")+
  theme_bw()

lp01| lp02

```

### Missing data: Uganda

```{r, error = F, message=F, warning = F}

missing_ds <- map(dsuga, ~mean(is.na(.))*100) 
missing_ds <- as.data.frame(missing_ds)
missing_ds <- as_tibble(cbind(variable = names(missing_ds), t(missing_ds)))
missing_ds$percent_missing <- missing_ds$V2
missing_ds$percent_missing <- as.numeric(missing_ds$percent_missing)

missing_ds <- select(missing_ds,-c(2))
missing_ds <- as.data.frame(missing_ds)
missing_ds$percent_missing <- as.numeric(missing_ds$percent_missing)
missing_ds <- as.data.table(missing_ds)

missing_ds_01 <- missing_ds[1:31,]
missing_ds_02 <- missing_ds[32:61,]

lp01 <- missing_ds_01 %>%
  lollipop_chart(x = variable,
                 y = percent_missing,
               line_color = "black",
               point_color = "black")+
  labs(y = "% missing data",
       x = "",
       title = "Uganda")+
  theme_bw()

lp02 <- missing_ds_02 %>% 
  lollipop_chart(x = variable,
                 y = percent_missing,
               line_color = "black",
               point_color = "black")+
  labs(y = "% missing data",
       x = "",
       title = "")+
  theme_bw()

lp01| lp02

```


### Missing data: full dataset

```{r, error = F, message=F, warning = F}

missing_ds <- map(ds, ~mean(is.na(.))*100) 
missing_ds <- as.data.frame(missing_ds)
missing_ds <- as_tibble(cbind(variable = names(missing_ds), t(missing_ds)))
missing_ds$percent_missing <- missing_ds$V2
missing_ds$percent_missing <- as.numeric(missing_ds$percent_missing)

missing_ds <- select(missing_ds,-c(2))
missing_ds <- as.data.frame(missing_ds)
missing_ds$percent_missing <- as.numeric(missing_ds$percent_missing)
missing_ds <- as.data.table(missing_ds)

missing_ds_01 <- missing_ds[1:31,]
missing_ds_02 <- missing_ds[32:61,]

lp01 <- missing_ds_01 %>%
  lollipop_chart(x = variable,
                 y = percent_missing,
               line_color = "black",
               point_color = "black")+
  labs(y = "% missing data",
       x = "",
       title = "Full dataset")+
  theme_bw()

lp02 <- missing_ds_02 %>% 
  lollipop_chart(x = variable,
                 y = percent_missing,
               line_color = "black",
               point_color = "black")+
  labs(y = "% missing data",
       x = "",
       title = "")+
  theme_bw()

lp01| lp02

```

# **Section 2: Demographics**

Demographic variables in the analysis:

- Age
- Gender
- Socio-economic status
- Religious affiliation
- Education **(NEEDS MAJOR WORK)**
- Marital status
- Ethnicity

## Variable: Sample size by Country

```{r, error = F, message = F, warning = F}

tbl01 <- table(ds$country)

## Table of user language by country:
tbl01

## Sample size by country:

lp01 <- ds %>% 
  # drop_na(Country) %>%
  lollipop_chart(x = country,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Sample size by country")+
  theme_bw()

lp01

```

## Variable: Age

```{r, error = F, message = F, warning = F}

summary(ds$age)

ds %>% drop_na(age)%>%
ggplot(aes(x = age))+
  geom_histogram(color = "black",
                 fill = "gray",
                 bins = 50)+
  geom_textvline(label = "Mean = 37.00", 
                 xintercept = 37.00, 
                 vjust = 1.1, 
                 lwd = 1.05, 
                 linetype = 2)+
  labs(x = "Age", 
       y = "Frequency", 
       title = "Age distribution (full sample)")+
  theme_bw()

ds %>% drop_na(age)%>%
ggplot(aes(x = age))+
  geom_histogram(color = "black",
                 fill = "gray",
                 bins = 50)+
  labs(x = "Age", 
       y = "Frequency", 
       title = "Age distribution by country")+
  facet_wrap(~country, nrow = 2)+
  theme_bw()


```

## Variable: Gender

```{r, error = F, message = F, warning = F}

lp02 <- ds %>% 
  drop_na(gender, age) %>%
lollipop_chart(x = gender,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Gender distribution (full sample)")+
#  facet_wrap(~Country, nrow = 2)+
  theme_bw()

lp02


bp01 <- ds %>% drop_na(gender, age) %>% 
  ggplot(aes(y = age, 
             x = gender))+
geom_boxplot(fill = "grey")+
  labs(y = "Age",
       x = "",
       title = "Age and gender distribution by country")+
  facet_wrap(~country, nrow = 2)+
  coord_flip()+
  theme_bw()

bp01

```

## Variable: Socio-economic status

```{r, error = F, message = F, warning = F}

ds %>% drop_na(ses) %>%
lollipop_chart(x = ses,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Socioeconomic status (full sample)")+
  theme_bw()


sesgmb <- dsgmb %>% drop_na(ses) %>%
lollipop_chart(x = ses,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Gambia")+
  theme_bw()


sespak <- dspak %>% drop_na(ses) %>%
lollipop_chart(x = ses,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Pakistan")+
  theme_bw()


sestza <- dstza %>% drop_na(ses) %>%
lollipop_chart(x = ses,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Tanzania")+
  theme_bw()

sesuga <- dsuga %>% drop_na(ses) %>%
lollipop_chart(x = ses,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Uganda")+
  theme_bw()

## All four plots together:

sesplot <- (sesgmb | sespak) / (sestza | sesuga) 

sesplot + plot_annotation("Socio-economic status by country")

```


## Variable: Marital status

```{r, error = F, message = F, warning = F}

ds %>% drop_na(married) %>%
lollipop_chart(x = married,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Marital status (full sample)")+
  theme_bw()

maritalgmb <- dsgmb %>% drop_na(married) %>%
lollipop_chart(x = married,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Gambia")+
  theme_bw()


maritalpak <- dspak %>% drop_na(married) %>%
lollipop_chart(x = married,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Pakistan")+
  theme_bw()


maritaltza <- dstza %>% drop_na(married) %>%
lollipop_chart(x = married,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Tanzania")+
  theme_bw()

maritaluga <- dsuga %>% drop_na(married) %>%
lollipop_chart(x = married,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Uganda")+
  theme_bw()

## All four plots together:

maritalplot <- (maritalgmb | maritalpak) / (maritaltza | maritaluga) 

maritalplot + plot_annotation("Marital status by country")

```

## Variable: Religious affiliation

```{r, error = F, message = F, warning = F}

lp05 <- ds %>% drop_na(religion) %>%
lollipop_chart(x = religion,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Religious distribution (full sample)")+
  theme_bw()

lp05


religiongmb <- dsgmb %>% drop_na(religion) %>%
lollipop_chart(x = religion,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Gambia")+
  theme_bw()


religionpak <- dspak %>% drop_na(religion) %>%
lollipop_chart(x = religion,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Pakistan")+
  theme_bw()


religiontza <- dstza %>% drop_na(religion) %>%
lollipop_chart(x = religion,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Tanzania")+
  theme_bw()

religionuga <- dsuga %>% drop_na(religion) %>%
lollipop_chart(x = religion,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Uganda")+
  theme_bw()

## All four plots together:

religionplot <- (religiongmb | religionpak) / (religiontza | religionuga) 

religionplot + plot_annotation("Religious affiliation by country")

```

## Variable: Education

**EDUCATION VARIABLE NEEDS A LOT OF WORK. SPECIFICALLY FOR GAMBIA AND TANZANIA**

```{r, error = F, message = F, warning = F}

# table(dsgmb$education)
# table(dspak$education)
# table(dstza$education)
# table(dsuga$education)

```


## Variable: Ethnicity

```{r, error = F, message = F, warning = F}

## Gambia:
eth <- as.data.frame(table(dsgmb$ethnicity))
eth$Var1 <- as.character(eth$Var1)
eth$ethnicity <- ifelse(eth$Freq < 2, "Other", eth$Var1)
l1 <- as.list(eth$ethnicity)

dsgmb2 <- dsgmb[, c("ethnicity")]

dsgmb2$ethnicity <- ifelse(dsgmb2$ethnicity %in% l1, dsgmb2$ethnicity, "Other")
dsgmb2$ethnicity <- ifelse(dsgmb2$ethnicity == "Serere", "Serer",
                 ifelse(dsgmb2$ethnicity == "", NA, dsgmb2$ethnicity))

ethgmb <- dsgmb2 %>% drop_na(ethnicity) %>%
lollipop_chart(x = ethnicity,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Gambia")+
  theme_bw()

## Pakistan:
eth <- as.data.frame(table(dspak$ethnicity))
eth$Var1 <- as.character(eth$Var1)
eth$ethnicity <- ifelse(eth$Freq < 7, "Other", eth$Var1)
l1 <- as.list(eth$ethnicity)

dspak2 <- dspak[, c("ethnicity")]

dspak2$ethnicity <- ifelse(dspak2$ethnicity %in% l1, dspak2$ethnicity, "Other")
dspak2$ethnicity <- ifelse(dspak2$ethnicity == "Urduspeaking", "Urdu speaking",
                 ifelse(dspak2$ethnicity == "", NA, dspak2$ethnicity))

ethpak <- dspak2 %>% drop_na(ethnicity) %>%
lollipop_chart(x = ethnicity,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Pakistan")+
  theme_bw()

## Tanzania:
eth <- as.data.frame(table(dstza$ethnicity))
eth$Var1 <- as.character(eth$Var1)
eth$ethnicity <- ifelse(eth$Freq < 7, "Other", eth$Var1)
l1 <- as.list(eth$ethnicity)

dstza2 <- dstza[, c("ethnicity")]

dstza2$ethnicity <- ifelse(dstza2$ethnicity %in% l1, dstza2$ethnicity, "Other")
dstza2$ethnicity <- ifelse(dstza2$ethnicity == "Serere", "Serer",
                 ifelse(dstza2$ethnicity == "", NA, dstza2$ethnicity))

ethtza <- dstza2 %>% drop_na(ethnicity) %>%
lollipop_chart(x = ethnicity,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Tanzania")+
  theme_bw()

## Uganda:
eth <- as.data.frame(table(dsuga$ethnicity))
eth$Var1 <- as.character(eth$Var1)
eth$ethnicity <- ifelse(eth$Freq < 7, "Other", eth$Var1)
l1 <- as.list(eth$ethnicity)

dsuga2 <- dsuga[, c("ethnicity")]

dsuga2$ethnicity <- ifelse(dsuga2$ethnicity %in% l1, dsuga2$ethnicity, "Other")
dsuga2$ethnicity <- ifelse(dsuga2$ethnicity == "japhadollah", "Japhadollah",
                    ifelse(dsuga2$ethnicity == "Atesot", "Iteso",
                    ifelse(dsuga2$ethnicity == "Etesot", "Iteso",
                    ifelse(dsuga2$ethnicity == "Itesot", "Iteso",
                    ifelse(dsuga2$ethnicity == "", NA, dsuga2$ethnicity)))))

ethuga <- dsuga2 %>% drop_na(ethnicity) %>%
lollipop_chart(x = ethnicity,
               line_color = "black",
               point_color = "black")+
  labs(y = "Frequency",
       x = "",
       title = "Uganda")+
  theme_bw()

## All four plots together:

ethplot <- (ethgmb | ethpak) / (ethtza | ethuga) 

ethplot + plot_annotation("Ethnic distribution by country")

```

# **Section 3. Measures of interest**

Variables of interest in this analysis: 

- Endorsement of Barrier Bound Leadership (BBL)
- Endorsement of Barrier Crossing Leadership (BCL)

- Imagistic items:
  - Event: Positive affect
  - Event: Negative affect
  - Event: Episodic recall
  - Event: Shared perception
  - Event: Reflection
  - Event: Transformative for individual
  - Event: Transformative for group
  
- Ingroup fusion
- Ingroup identification
- Outgroup fusion
- Outgroup identification
- Perception of religious freedom
- Experience of religious freedom
- Empathic concern
- Perspective taking
- Perceived history of discrimination
- Frequency of positive contact with OG
- Frequency of negative contact with OG
- Outgroup cooperation
- Outgroup hostility
- Willingness to fight outgroup

- Outgroup affect (made up of five sub-items)

# **Section 3b: Outgroup attitudinal measures **

### Perceived history of discrimination

```{r, error = F, message = F, warning = F}

# single item measure

ogp01 <- ds %>% drop_na(history_discrimination) %>% 
  ggplot(aes(y = history_discrimination, 
             x = country))+
geom_boxplot(fill = "grey")+
  labs(y = "Perceived discrimination",
       x = "",
       title = "Perceived history of discrimination by country")+
  #facet_wrap(~country, nrow = 2)+
  coord_flip()+
  theme_bw()

ogp01

```


### Positive contact with outgroup:

```{r, error = F, message = F, warning = F}

# single item measure

ogp02 <- ds %>% drop_na(freq_positive_contact) %>% 
  ggplot(aes(y = freq_positive_contact, 
             x = country))+
geom_boxplot(fill = "grey")+
  labs(y = "Frequency",
       x = "",
       title = "Positive contact with outgroup by country")+
  #facet_wrap(~country, nrow = 2)+
  coord_flip()+
  theme_bw()

ogp02

```


### Negative contact with outgroup:

```{r, error = F, message = F, warning = F}

# single item measure

ogp03 <- ds %>% drop_na(freq_negative_contact) %>% 
  ggplot(aes(y = freq_negative_contact, 
             x = country))+
geom_boxplot(fill = "grey")+
  labs(y = "Frequency",
       x = "",
       title = "Negative contact with outgroup by country")+
  #facet_wrap(~country, nrow = 2)+
  coord_flip()+
  theme_bw()

ogp03

```


### Willingness to fight outgroup:

```{r, error = F, message = F, warning = F}

# single item measure

ogp04 <- ds %>% drop_na(fight_outgroup) %>% 
  ggplot(aes(y = fight_outgroup, 
             x = country))+
geom_boxplot(fill = "grey")+
  labs(y = "Willingness",
       x = "",
       title = "Willingness to fight outgroup by country")+
  #facet_wrap(~country, nrow = 2)+
  coord_flip()+
  theme_bw()

ogp04

```


### Outgroup hostility:

```{r, error = F, message = F, warning = F}
# 2 items make up full scale:
# og_host_01
# og_host_02

ogp05 <- ds %>% drop_na(og_hostility) %>% 
  ggplot(aes(y = og_hostility, 
             x = country))+
geom_boxplot(fill = "grey")+
  labs(y = "Hostility",
       x = "",
       title = "Outgroup hostility by country")+
  #facet_wrap(~country, nrow = 2)+
  coord_flip()+
  theme_bw()

ogp05

```

### Outgroup cooperation:

```{r, error = F, message = F, warning = F}

# 2 items make up full scale:
# og_coop_01
# og_coop_02

ogp06 <- ds %>% drop_na(og_cooperation) %>% 
  ggplot(aes(y = og_cooperation, 
             x = country))+
geom_boxplot(fill = "grey")+
  labs(y = "Cooperation",
       x = "",
       title = "Outgroup cooperation by country")+
  #facet_wrap(~country, nrow = 2)+
  coord_flip()+
  theme_bw()

ogp06

```


### Outgroup affect:

```{r, error = F, message = F, warning = F}

# 5 items make up full scale:

#NegativeToPositive
#HostileToFriendly
#SuspiciousToTrusting
#ContemptToRespect
#ThreatenedToRelaxed


ogp07 <- ds %>% drop_na(og_affect) %>% 
  ggplot(aes(y = og_affect, 
             x = country))+
geom_boxplot(fill = "grey")+
  labs(y = "Affect",
       x = "",
       title = "Outgroup affect by country")+
  #facet_wrap(~country, nrow = 2)+
  coord_flip()+
  theme_bw()

ogp07

```


# **Section 4: TO DO**

- Replicate Table 2 from paper 1 for all of the above variables
  - This is quite easy. Copy R code from one of the individual country Rpubs files.

- Replicate Figure 6 from Paper 1
  - This will take a bit of work.
 
- Replicate Table 3 from paper 1 (CFA for BCL and BBL)  
  - Done. See section 5 below

- Replicate Table 4 from paper 1 (CFA for imagistic items)
  
- Replicate Table 5 from paper 1 (Standardized Loadings from Three Factor EFA)

- Replicate Table 6 from paper 1 (CFA for Fusion/Identification measures)
  - Done. See sections 6 and 7 below

- Everything else from Table 6 onwards... 

# **Section 5: EFA and CFA: BCL and BBL**

## EFA:

```{r, error = F, message = F, warning = F}

leadership <- cbind.data.frame(ds$ENDBCL01, ds$ENDBCL02, ds$ENDBCL03, 
                               ds$ENDBBL01, ds$ENDBBL02, ds$ENDBBL03)

leadership <- na.omit(leadership)

scree(leadership)

fit02 <- factanal(leadership, 2, rotation="promax")
fit02

```

## CFA: 

```{r, error = F, message = F, warning = F}

## Remove 'ds$END' from variable names:
names(leadership) <- sub(".*\\END", "", names(leadership))

#correlated two factor solution, marker method
twofacs <- 'BCL =~ BCL01+BCL02+BCL03
            BBL =~ BBL01+BBL02+BBL03' 

cfa02 <- cfa(twofacs, 
             data=leadership, 
             std.lv=TRUE) 

summary(cfa02,
        fit.measures=TRUE,
        standardized=TRUE)

```

# **Section 6: EFA and CFA: Ingroup Fusion and Identification**

## EFA

```{r, error = F, message = F, warning = F}

## IG IGbonds dataframe:
IGbonds <- cbind.data.frame(ds$IGF01, ds$IGF02, ds$IGF03,
                            ds$IGI01, ds$IGI02, ds$IGI03)

names(IGbonds) <- sub('ds\\$', '', names(IGbonds))

IGbonds <- na.omit(IGbonds)

scree(IGbonds)

fit02 <- factanal(IGbonds, 2, rotation="promax")
fit02

```

## CFA

```{r, error = F, message = F, warning = F}

#correlated two factor solution, marker method
twofacs <- 'IGFusion =~ IGF01+IGF02+IGF03
            IGIdentification =~ IGI01+IGI02+IGI03' 

cfa02 <- cfa(twofacs, 
             data=IGbonds, 
             std.lv=TRUE) 

summary(cfa02,
        fit.measures=TRUE,
        standardized=TRUE)

```


# **Section 7: EFA and CFA: Outgroup Fusion and Identification**

## EFA

```{r, error = F, message = F, warning = F}

## OG OGbonds dataframe:
OGbonds <- cbind.data.frame(ds$OGF01, ds$OGF02, ds$OGF03,
                            ds$OGI01, ds$OGI02, ds$OGI03)

names(OGbonds) <- sub('ds\\$', '', names(OGbonds))

OGbonds <- na.omit(OGbonds)

scree(OGbonds)

fit02 <- factanal(OGbonds, 2, rotation="promax")
fit02

```

## CFA

```{r, error = F, message = F, warning = F}

#correlated two factor solution, marker method
twofacs <- 'OGFusion =~ OGF01+OGF02+OGF03
            OGIdentification =~ OGI01+OGI02+OGI03' 

cfa02 <- cfa(twofacs, 
             data=OGbonds, 
             std.lv=TRUE) 

summary(cfa02,
        fit.measures=TRUE,
        standardized=TRUE)

```

# **Section 8: EFA and CFA: Imagistic items (after removing certain items)**

## EFA

```{r, error = F, message = F, warning = F}

imagistic <- cbind.data.frame(ds$event_episodic_recall_01, 
                              ds$event_episodic_recall_02,
                              ds$event_shared_perception_01, 
                              ds$event_shared_perception_02,
                              ds$event_reflection_01, 
                              ds$event_reflection_02,
                              ds$event_transformative_indiv_01,
                              #ds$event_transformative_indiv_02,
                              ds$event_transformative_group_01
                              #ds$event_transformative_group_02
                              )

```

# **Section 8: EFA: Imagistic items**

```{r, error = F, message = F, warning = F}

imagistic <- cbind.data.frame(ds$event_episodic_recall_01, 
                              ds$event_episodic_recall_02,
                              ds$event_shared_perception_01, 
                              ds$event_shared_perception_02,
                              ds$event_reflection_01, 
                              ds$event_reflection_02,
                              #ds$event_transformative_indiv_01,
                              ds$event_transformative_indiv_02,
                              #ds$event_transformative_group_01,
                              ds$event_transformative_group_02
                              )
names(imagistic) <- sub('ds\\$event\\_', '', names(imagistic))

imagistic <- na.omit(imagistic)

mtx <- cor(imagistic[, c(1:8)])

```

### Correlation plot:

```{r, error = F, message = F, warning = F}

corrplot(mtx, method = "number", number.cex = 0.7,
         col=c("darkred", "red", "red",
               "darkgrey", "blue", "darkblue"))

```

### Scree plot:

```{r, error = F, message = F, warning = F}

scree(imagistic)

```

### Four factor model:

```{r, error = F, message = F, warning = F}

fit04 <- factanal(imagistic, 4, rotation="promax")

print(fit04$loadings, cutoff = 0.35)

```

### Three factor model:

```{r, error = F, message = F, warning = F}

fit03 <- factanal(imagistic, 3, rotation="promax")

print(fit03$loadings, cutoff = 0.35)

```

# **Section 9: CFA: Imagistic items**

```{r, error = F, message = F, warning = F}

## Remove 'ds$END' from variable names:
names(imagistic) <- sub(".*\\$", "", names(imagistic))

names(imagistic)

#correlated two factor solution, marker method
fourfacs <- 'Reflection =~ reflection_01+reflection_02
             Vivid_recall =~ episodic_recall_01+episodic_recall_02
             Perceived shareness =~ shared_perception_01+shared_perception_02
             Defining_experience =~ transformative_indiv_02+transformative_group_02' 

cfa04 <- cfa(fourfacs, 
             data=imagistic, 
             std.lv=TRUE) 

summary(cfa04,
        fit.measures=TRUE,
        standardized=TRUE)

```



